### 2023-01-26 review_answers.md

# Review 1

* **169**: *Example 5 is not aligned*

	* There is nothing that could be “aligned” in this example. I interpreted it as "make the distance between object language and translation identical to example 4", and added translations for all wordforms in the paradigm.

* **188**: *The author Alves Chagas (2013) is known as Chagas (2013)*

	* I've changed the name.

# Review 2

* **Overall**: *My major concern has to do with the reconstructed Proto-Pekodian forms of verbs. Although
some sound correspondences between Bakairi and Ikpeng have been identified in Meira & Franchetto (2005), I am not aware of any existing study that would address the phonological
reconstruction of Proto-Pekodian. This is important because not all assertions regarding
cognacy are equally convincing. For instance, it is not obvious to this reviewer that
Proto-Pekodian *-ɨtən- is a valid reconstruction, and that the purported reflexes of this form
are exact cognates: Ikpeng -aran- seems to point to *-ətən-, Bakairi t, as opposed to *d,
points to an erstwhile consonant cluster (*wɨ-wtə-?); the Arara form could be cognate with
the Bakairi counterpart, but not with the Ikpeng one. If the Ikpeng form is actually
noncognate, the author’s calculations in Part 2 would have to be redone. The irregular
correspondences between -iptoŋ- and -ɨtəgɨ- are likewise suspect. I’d like the author to
include a section, or maybe an appendix, explaining the basic premises of their
reconstruction of Proto-Pekodian.*

	* TBD

* **Overall**: *Another suggestion, which is easier to implement but is perhaps somewhat more radical, is
to split the manuscript in two. Since the author’s calculations in Part 2 are entirely dependent
on the correctness of their findings in Part 1, and since the methodologies employed in these
two parts of the manuscripts are entirely different (comparative method + Diachronic
Construction Grammar vs. quantitative study), I’d recommend the author to consider the
possibility to publish their Part 2 as a separate paper, possibly in a journal specializing on
quantitative linguistics (though of course it still lies within Cadernos’ scope), since its
methodology could be of interest to readers that outside the Americanist community. I leave
this to the author’s discretion.*

	* TBD

* **Data**: *The author reports that no first-person forms of the Ikpeng verb for ‘to go down’ are attested,
with a reference to Angela Chagas. I am not a specialist on Ikpeng, but I have just asked aIkpeng acquaintance (whose name is Fael Ikpeng in the case the author would like to
acknowledge his help), and he gave me the form iptongtxi (∅-iptoŋ-tʃi) for ‘I’ll go down’,
which fits nicely the author’s predictions.*

	* TBD

* **Thoughout**: *The use of ‘to’ in the English glosses of verbs is non-consistent. Please either use it
in all glosses or leave it out.*

	* TBD

* **Throughout**: *For languages with significant dialectal variation, such as Kari’ña or Bakairi, please
indicate the dialect from which a given datum was extracted. For example, it would
be important to know whether Bakairi k-əewɨ- belongs to a dialect that lost
intervocalic rhotics (this would make its derivation from *-ət-epɨ- more credible).*

	* TBD

* **Figure 1**: *Trinidad and Tobago is missing*

	* TBD

* **Figure 1**: *Extinct languages are not shown. If this is on purpose, please modify the label, but I
believe it is important for the reader to know that there used to be Cariban languages
outside the current Cariban-speaking area, such as Pimenteira in Piauí, Cumanagoto
and other groups on the Caribbean coast, and Kari’ña varieties in the Antilles and in
Trinidad.*

	* TBD

* **Figure 1**: *Languages such as Kari’ña really should be represented by meshes/polygons rather
than by points. Bakairi, Upper Xingu Carib, and other languages could be best
represented by several points.*

	* TBD

* **Figure 1**: *The spelling Kapón is not particularly common as opposed to the more common
Kapong (or Akawaio, or Ingarikó).*

	* TBD

* **footnote 1**: *“The presence of a 1+2 person value implies that of a 1+3 value” — I’d leave this out.
In fact, there are many languages where 1+2 exists as a category, but 1+3 isn’t
encoded differently from 1 (which has led some linguists to refer to 1+2 as “the fourth
person”).*

	* TBD

* **footnote 1**: *“Further, TAM suffixes in the attested forms are omitted, since a) the focus lies on the
prefixes and stems, and b) full paradigms with the same TAM suffix are rare in the
available sources” — the justification is legitimate, but the reader might want to know
whether different TAM configurations imply different person indexing patterns, as they
often do. It is often the case that different participants (say, A vs. P) are indexed in
the same affix slot under different TAM values in some languages, and even for the
same notional participant different prefixes (belonging to different sets) may occur. A
clarification is needed on which TAM values are seen as representative in your paper
–– I assume you only consider the ones that select for Gildea’s Set I.*

	* TBD

* **footnote 1**: *“Standard IPA symbols are used in the transcription of Cariban languages” →
“Standard IPA symbols are used for linguistic data” — you also use IPA for Germanic
languages*

	* TBD

* **footnote 1**: *“In languages with strong morphophonological processes and/or non-phonemic
orthography...” — I would make this uniform across the paper, when possible. It would be more reader-friendly if you either systematically included the contemporary
orthographic representation or always left it out. The inconsistency looks particularly
out of place in the Hixkaryana data in 11b–c, and in the Kari’ña examples in 2a–b. I
understand that different sources use different transcription systems, but I have no
doubt that the author has the necessary knowledge to easily convert between
orthographies — could you maybe always follow the conventions used by the
speakers?*

	* TBD

* **footnote 1**: *“Gildea (2018) is followed in using ⟨ə⟩ for the Proto-Cariban reconstructed by Meira &
Franchetto (2005)” → “Gildea (2018) is followed in using ⟨ə⟩ for the Proto-Cariban *ô
reconstructed by Meira & Franchetto (2005)”*

	* TBD

* **section 2.1**: *Consider defining “locuphoric” and “aliophoric”. This reviewer is familiar with
Haspelmath’s preferred terminology, but the reader cannot be expected to — Gildea (1998)
does not use these terms for obvious reasons, and a search on Google returns 14 results for
“aliophoric”. Also note that you use “aliophoric” and “nonlocal” within the same period,
though Haspelmath’s intention was to altogether replace the term “nonlocal” with
“aliophoric”.*

	* TBD

* **lines 60–61**: *Don’t use hyphens for morpheme segmentation within glosses*

	* TBD

* **Figure 2**: *Does Werikyana really lack the (j) in 2SP.P before vowel-initial stems? Does the j-
element actually always show up after owɨ(ro)-, or should it be parenthesized? (also in line
5 of example 1)*

	* TBD

* **line 107**: *Consider defining the term “deverbalized” (does this encompass all nonfinite
forms?), which will be relevant for the reader’s comprehension of the paradigm of the
Proto-Cariban verb for ‘to go’.*

	* TBD

* **between lines 110 and 111 (also 114–121)**: *“In modern instantiations of Cariban split-S,
mismatches between the semantics of verbs and their SA or SP status are common,
exemplified with Kari’ña data in (2)” — This piece of discussion strikes me as a strawman
fallacy, at least the way it is phrased in the current version of the manuscript. It is by now a
well-established fact that split-S does not typically show a 100% Guarani-like correlation with
semantics in many languages, so I can’t see why one would expect there to be such a
correlation in Cariban. If you are contesting claims found in earlier literature, consider citing
them.*

	* TBD

* **lines 127–8**: *“although their reflexes on verbs have been merged into a single morpheme in
modern languages” → “although their reflexes on verbs have been merged into a single
morpheme in some modern languages”*

	* TBD

* **example 4**: *Consider segmenting the TAM suffixes off the roots so as to facilitate the
recognition of cognate roots across Pekodian*

	* TBD

* **example 7d**: *k-ɨtəgɨ-se cannot seem to be a correct restitution of ⟨kχ-itaké-he⟩. Is this an
instance of Proto-Bakairi *ʔs, as reconstructed by Meira (2005), which is reflected as ʔ in
Western Bakairi and as s in Eastern Bakairi?*

	* TBD

* **Section 3.1.1**: *It should be made clear at this point that the discussion of the reconstructed
forms is postponed to Section 3.2, otherwise the reader is left wondering whether the
author’s cognacy judgments can be trusted.*

	* TBD

* **Table 6**: *Consider replacing *w-epɨ- with *w-(əd-)epɨ-. The form *w-əd-epɨ- certainly existed
in Proto-Pekodian, since it has exact cognates elsewhere in Cariban.*

	* TBD

* **Table 8**: *Asterisks are missing in PW forms.
example 11: consider swapping (c) and (d)*

	* TBD

* **line 239**: *“a fossilized of the SA class marker” → “a fossilized SA class marker” (incidentally,
why not consider it a nonfiniteness prefix/nominalizer? “Class marker” is not a transparent
choice, especially if the morpheme in question only shows up in nonfinite forms in PC.)*

	* TBD

* **line 240**: *“the first person form Hixkaryána ‘to go’” — consider rephrasing this
footnote 8: “Here, both Tiriyó əepɨ and Akuriyó eepɨ are identified as reflecting *ətepɨ
(Section 3.2.4), via Proto-Taranoan *(ət͡ʃ-)epɨ and Proto-Tiriyoan *(əʔ)epɨ” — Why the
element *ət- is segmented (and parenthesized) in the Proto-Taranoan and Proto-Tiriyoan
forms, but not in the Proto-Cariban one?*

	* TBD

* **example 12**: *I fail to see what does the example 12a illustrate. If anything, *w is not lost in it.*

	* TBD

* **example 13**: *The form p-ɨ(h)tə- should be discussed in 3.1.3, on Tiriyoan, and not in 3.1.4,
on Akuriyó, since this form is also attested in Tiriyó.*

	* TBD

* **example 15**: *Apart from non-uniform transcription systems (IPA in (a–b), orthography in (c));
-e is glossed as NPST in (a–b), but as NPST.CERT in (c) — is this correct?*

	* TBD

* **lines 332–4**: *“a choice not only motivated by a desire to avoid an idiosyncratic intransitive
first person prefix ɨ- instead of regular kɨ-” — the period is unfinished*

	* TBD

* **Table 15 and subsequent tables**: *This reviewer doesn’t think the aligned presentation of
data contributes much to the discussion — on the contrary, it confuses the reader. Even
though I am familiar with List’s ideology on this matter, the presentation scheme is
suboptimal for presenting allomorphy (ke/ge in Pekodian), and obfuscates the identity
correspondence between PC *ati (and its reflexes) and Pekodian e, Kuhikugu/Kalapalo/Matipu i (I assume *aCi > *ai > *e > Pekodian e, UXC i).*

	* TBD

* **lines 373–375**: *“Since many languages only show ɨ in certain contexts, even forms like Tiriyó
wɨtənne ‘I went’ (Meira 1999: 43) are ambiguous, since epenthetic ɨ breaks up CC clusters
on prefix-verb boundaries” — consider rephrasing this so as to avoid two since-clauses.*

	* TBD

* **example 20**: *I can’t see why would you want to you a two-lines presentation of the data,
since there are no “strong morphophonological processes and/or non-phonemic
orthography” involved.*

	* TBD

* **footnote 13**: *“final ŋ in Proto-Xinguan”: an asterisk is missing. In addition, the explanation
given is a non-explanation. Couldn’t PX *-ŋ be a previously unnoticed retention from
Proto-Cariban?*

	* TBD

* **lines 498–499**: *“These verbs formed a lexical connection with prototypical members of the
group, developing new past tense forms as a result” — did you mean ‘patient participle’?
section 4: Please justify the choice of Apalaí texts for the frequency count — why not the
exceptionally-well described Kari’ña? It is true that there are no ready-to-use corpora for
Cariban languages, but there are many glossed texts available. Another good start would be
the Kuhikugu and Kalapalo texts in Stenzel & Franchetto (2017).
section 4: In frequency counts, it should be made clear if one counts the frequency of
verbal lexemes or specifically of verbs inflected for 1st person (some verb may only be
frequent in the 3rd person).*

	* TBD

* **Abbreviations**: *“S marked like A” → “S marked more like A than like P” (?)*

	* TBD

* **References**: *consider citing the recently published version of Cáceres and Gildea’s
Amazonicas presentation on Tense-Aspect constructions in Yawarana (<http://www.etnolinguistica.org/article:vol10n1-7>).*

	* TBD

* **lines 29–30**: *“like in Tables 1 and 2 .” — remove the space*

	* TBD

* **Table 22**: *something is wrong with the table’s width and the layout of the label*

	* TBD

* **Abbreviations**: *uncertainty.9 → uncertainty.*

	* TBD

* **References**: *(Franchetto 1986): Estudo Etnolinguistico → Estudo etnolinguístico*

	* TBD

* **References**: *The use of capital letters in Spanish and Portuguese titles is inconsistent.*

	* TBD

### 2023-08-04 documents/sections/extensions.tex
font, 'alignment'
implemented all recommendations from review 1
readthrough

\subsubsection{\PPek \rc{k-}}
\label{sec:pekodian}
%The Pekodian branch was suggested by \textcite{meira2005southern}, as the result of fieldwork on \bakairi by Meira and the availability of more material on \ikpeng. % \parencites{pacheco1997relativizacao}{ikpengpacheco1997}{campetela1997analise}{pacheco1998nominalizacao}{ikpengpacheco2001}{campetela2002aspectos}{pacheco2002aspectos}{pacheco2003intransitivos}.
The Pekodian branch consists of closely related \arara and \ikpeng, with \bakairi as a more distant member.
The contribution establishing the branch \parencite{meira2005southern} focused on phonology and lexicon, so no reconstructions of \PPek morphosyntax are found in the literature.
However, all three Pekodian languages have a regular \gl{1}\gl{s_a_} marker \obj{k-} \pcref{tab:pekreg}, allowing the reconstruction of a \PPek \gl{1}\gl{s_a_} marker \rc{k-}.

@@

The most detailed description of a Pekodian language \parencite{alves2017arara} names six%
\footnote{Seven in her analysis, treating the two meanings of \obj{it͡ʃi} \qu{to be, to lie down} as different verbs.}
\arara \gl{s_a_} verbs forming a subclass defined by a first person marker \obj{w(ɨ)-} rather than \obj{k-}, shown in \exref{arairr}.
There is also a reflex of the copula \rc{a[p]} \pcref{sec:be}, serving syntactically as a postposition introducing adverbial clauses meaning \qu{if} or \qu{when} \parencite[199--201]{alves2017arara}.
However, it inflects with verbal \setone prefixes, including first person \obj{w-} \exref{araap}.
%We take these \arara verbs as a starting point for the other Pekodian languages, as \textcite{alves2017arara} gives the most detailed description of person markers for any language of the branch.

@@

\ex<araap> \arara \parencite[200]{alves2017arara}\\
\begin{tabular}[t]{@{}ll@{}}
\gl{1} & \obj{w-aptam} \qu{when/if I was}\\
\gl{2} & \obj{m-od-aptam}\\
\gl{1+2} & \obj{kud-aptam}\\
\gl{3} & ∅\obj{-aptam}\\
\end{tabular}
\xe
\end{multicols}

@@

\subsubsection{\yukpa \obj{j-}}
\label{sec:yukpa}
The divergent nature of \yukpa\footnote{Very little is known about its sister \japreria, whose status as a dialect of \yukpa is contested by \textcite{oquendo2004japreria}.} is \textit{inter alia} visible in the loss of many \setone forms and the formation of non-cognate innovative constructions \parencite{meira2006syntactic}.
However, it does preserve the \setone prefixes in the immediate past, which shows a unified intransitive paradigm \pcref{tab:yukreg}.
The wholesale loss of \gl{1+2} as an inflectional value was combined with the extension of \gl{2}\gl{s_a_} \obj{m(ɨ)-} to (now former) \gl{s_p_} verbs like \obj{nɨ} \qu{to sleep}.
%
\input{floats/yukreg}%
%
These verbs share their first person marker \obj{j(ɨ)-} with former \gl{s_a_} verbs like \obj{otum} \qu{to wash self}, identifiable by their semantics and the reflex of \detrz.
Since \obj{j(ɨ)-} is the reflex of the \PC \gl{1}S\textsubscript{(P)} marker \rc{u(j)-} \parencite[92]{gildea1998}, it also occurs on transitive verbs in \gl{3}>\gl{1} scenarios \exref{yukpatr.yuk-5}.
In contrast, \gl{1}>\gl{3} scenarios are zero-marked \exref{yukpatr.yuk-1}.

@@

In intransitive verbs, this first-person zero marking is attested with a single verb, \obj{to} \qu{to go} \exref{yuk-7}.
It diverges from regular C-initial verbs with \obj{jɨ-}, like \qu{to sleep} \pcref{tab:yukreg}.
It can thus be identified as having resisted the extension of \obj{j-} in \yukpa.

>>>>

\subsubsection{\PPek \rc{k-}}
\label{sec:pekodian}
%The Pekodian branch was suggested by \textcite{meira2005southern}, as the result of fieldwork on \bakairi by Meira and the availability of more material on \ikpeng. % \parencites{pacheco1997relativizacao}{ikpengpacheco1997}{campetela1997analise}{pacheco1998nominalizacao}{ikpengpacheco2001}{campetela2002aspectos}{pacheco2002aspectos}{pacheco2003intransitivos}.
The Pekodian branch consists of closely related \arara and \ikpeng, with \bakairi as a more distant member.
\textcite{meira2005southern}, who established the branch, focused on phonology and lexicon, so no reconstructions of \PPek morphosyntax are found in the literature.
However, all three Pekodian languages have a regular \gl{1}\gl{s_a_} marker \obj{k-} \pcref{tab:pekreg}, allowing the reconstruction of a \PPek \gl{1}\gl{s_a_} marker \rc{k-}.

@@

The most detailed description of a Pekodian language \parencite{alves2017arara} names six%
\footnote{Seven in her analysis, treating the two meanings of \obj{it͡ʃi} \qu{to be / to lie down} as different verbs.}
\arara \gl{s_a_} verbs forming a subclass defined by a first person marker \obj{w(ɨ)-} rather than \obj{k-}, shown in \exref{arairr}.
There is also a reflex of the copula \rc{a[p]} \pcref{sec:be}, serving syntactically as a postposition introducing adverbial clauses meaning \qu{if} or \qu{when} \parencite[199--201]{alves2017arara}.
However, it inflects with verbal \setone prefixes, including first person \obj{w-} \exref{araap}.
%We take these \arara verbs as a starting point for the other Pekodian languages, as \textcite{alves2017arara} gives the most detailed description of person markers for any language of the branch.

@@

\ex<araap> \arara \parencite[200]{alves2017arara}\\
\begin{tabular}[t]{@{}lll@{}}
\gl{1} & \obj{w-aptam} & \qu{when/if I was}\\
\gl{2} & \obj{m-od-aptam} & \qu{when/if you were}\\
\gl{1+2} & \obj{kud-aptam} & \qu{when/if we were}\\
\gl{3} & ∅\obj{-aptam} & \qu{when/if s/he was}\\
\end{tabular}
\xe
\end{multicols}

@@

\subsubsection{\yukpa \obj{j-}}
\label{sec:yukpa}
The divergent nature of \yukpa\footnote{Very little is known about its sister \japreria, whose status as a dialect of \yukpa is contested by \textcite{oquendo2004japreria}.} is \textit{inter alia} visible in the loss of many \setone forms and the formation of non-cognate innovative main clause verbal constructions \parencite{meira2006syntactic}.
However, it does preserve the \setone prefixes in the immediate past, which shows a unified intransitive paradigm \pcref{tab:yukreg}.
The wholesale loss of \gl{1+2} as an inflectional value was combined with the extension of \gl{2}\gl{s_a_} \obj{m(ɨ)-} to (now former) \gl{s_p_} verbs like \obj{nɨ} \qu{to sleep}.
%
\input{floats/yukreg}%
%
These verbs share their first person marker \obj{j(ɨ)-} with former \gl{s_a_} verbs like \obj{otum} \qu{to wash self}, identifiable by their semantics and the reflex of \detrz.
Since \obj{j(ɨ)-} is the reflex of the \PC \gl{1}S\textsubscript{(P)} marker \rc{u(j)-} \parencite[92]{gildea1998}, it also occurs on transitive verbs in \gl{3}>\gl{1} scenarios \exref{yukpatr.yuk-5}.
In contrast, \gl{1}>\gl{3} scenarios are zero-marked \exref{yukpatr.yuk-1}.

@@

Zero-marked first person is attested for a single intransitive verb, \obj{to} \qu{to go} \exref{yuk-7}.
It diverges from regular C-initial verbs with \obj{jɨ-}, like \qu{to sleep} \pcref{tab:yukreg}.
It can thus be identified as having resisted the extension of \obj{j-} in \yukpa.

### 2023-08-04 documents/sections/introduction.tex
readthrough

In some Cariban languages, a small group of verbs show a divergent first person inflection pattern, a topic which has not received much attention in the literature.
This is illustrated for \hixka in \cref{tab:hixintro},\footnote{The presence of a \gl{1+2} person value implies that of a \gl{1+3} value.
This is usually expressed with a free pronoun combined with third person morphology in Cariban languages, so it is not represented as a distinct value in \cref{tab:hixintro} and other paradigm tables.
Further, TAM suffixes in the attested forms are omitted, since a) the focus lies on the prefixes and stems, and b) full paradigms with the same TAM suffix are rare in the available sources.
Standard IPA symbols are used in the transcription of Cariban languages, except for coronal rhotics, which are simply represented with \ort{r}, rather than \ort{ɽ} for \wayana or \ort{ɾ̠} for \maqui etc.
In languages with strong morphophonological processes and/or non-phonemic orthography the original form is shown in an additional line when presented in interlinearized examples.
\textcite{gildea2018reconstructing} is followed in using \ort{ə} for the \PC reconstructed by \textcite{meira2005southern}, although it was likely more back \parencite{gildea2010story}.}
with paradigms of four verbs, all members of the \gl{s_a_} inflectional class.
In this language, the verb \qu{to be} diverges from other \gl{s_a_} verbs like \qu{to fall} by having a first person marker \obj{w-}, rather than \obj{k-}.
A similar pattern exists in \trio \pcref{tab:triintro}, where the verb \qu{to go} has a first-person prefix \obj{wɨ-} while other \gl{s_a_} verbs have a prefix with phonologically conditioned allomorphs \envr{\obj{t-}}{\obj{ə}} and \envr{\obj{s-}}{\obj{e}}.
In both languages, the first person prefix of the verbs on the left is representative for the vast majority of \gl{s_a_} verbs.
%In both languages, there are only a few other verbs inflected identically to the divergent ones on the right; for example, the first-person form of \trio \qu{to be} is \obj{w-ei-} \parencites[339]{triomeira1999}.

Such divergent verbs have been identified for \hixka \parencite[188]{hixkaryanaderby1985}, \waiwai \parencite[90]{gildea1998}, the three Taranoan languages \parencite[112--115]{meira1998proto}, \bakairi \parencite{meira2003bakairi}, and \arara \parencite[153]{alves2017arara}, but have only been subject to comparative scrutiny in \posscite{meira1998proto} reconstruction of \PTar.
In synchronic analyses, these verbs and their first person prefixes may be called \firstmention{irregular}, contrasting with regular prefixes (like \hixka \obj{kɨ-} and \trio \obj{t-}/\obj{s-}) on regular verbs.
Note that there is no widely accepted definition of irregularity \parencite{stolz2012introduction}, and many stricter definitions \parencite[e.g.,][]{haspelmath2010understanding} require the pattern to occur at a single place in the grammar.
In such approaches, the verbs simply belong to a small inflectional (sub-)class, an analysis applied to the Pekodian languages \bakairi and \arara \parencites[4]{meira2003bakairi}[149]{alves2017arara}.

>>>>

In some Cariban languages, a small group of verbs show a divergent first person inflection pattern, a topic which has not received much attention in the literature.
This is illustrated for \hixka in \cref{tab:hixintro},\footnote{The presence of a \gl{1+2} person value implies that of a \gl{1+3} value.
This is usually expressed with a free pronoun combined with third person morphology in Cariban languages, so it is not represented as a distinct value in \cref{tab:hixintro} and other paradigm tables.
Further, TAM suffixes in the attested forms are omitted, since a) the focus lies on the prefixes and stems, and b) full paradigms with the same TAM suffix are rare in the available sources.
Standard IPA symbols are used in the transcription of Cariban languages, except for coronal rhotics, which are simply represented with \ort{r}, rather than \ort{ɽ} for \wayana or \ort{ɾ̠} for \maqui etc.
In languages with strong morphophonological processes and/or non-phonemic orthography the original form is shown in an additional line when presented in interlinearized examples.
\textcite{gildea2018reconstructing} is followed in using \ort{ə} for the \PC reconstructed by \textcite{meira2005southern}, although it was likely more back \parencite{gildea2010story}.}
with paradigms of four verbs, all members of the \gl{s_a_} inflectional class.
In this language, the verb \qu{to be} diverges from other \gl{s_a_} verbs like \qu{to fall} by having a first person marker \obj{w-}, rather than \obj{k-}.
A similar pattern exists in \trio \pcref{tab:triintro}, where \gl{s_a_} verbs have a prefix with phonologically conditioned allomorphs \envr{\obj{t-}}{\obj{ə}} and \envr{\obj{s-}}{\obj{e}}, while the verb \qu{to go} has a first-person prefix \obj{wɨ-}.
For both languages, the first person prefix on the first four verbs in the table is representative for the vast majority of \gl{s_a_} verbs.
%In both languages, there are only a few other verbs inflected identically to the divergent ones on the right; for example, the first-person form of \trio \qu{to be} is \obj{w-ei-} \parencites[339]{triomeira1999}.

Such divergent verbs have been identified for \hixka \parencite[188]{hixkaryanaderby1985}, \waiwai \parencite[90]{gildea1998}, the three Taranoan languages \parencite[112--115]{meira1998proto}, \bakairi \parencite{meira2003bakairi}, and \arara \parencite[153]{alves2017arara}, but have only been subject to comparative scrutiny in \posscite{meira1998proto} reconstruction of \PTar.
In synchronic analyses, these verbs and their first person prefixes may be called \firstmention{irregular}, contrasting with regular prefixes (like \hixka \obj{kɨ-} and \trio \obj{t-}/\obj{s-}) on regular verbs.
Note that there is no widely accepted definition of irregularity \parencite{stolz2012introduction}, and many stricter definitions \parencite[e.g.,][]{haspelmath2010understanding} require the pattern to occur at a single place in the grammar.
In such approaches, these verbs simply belong to a small inflectional (sub-)class, an analysis applied to the Pekodian languages \bakairi and \arara \parencites[4]{meira2003bakairi}[149]{alves2017arara}.
